---
title: "Case Study"
author: "Charbel Berkachi"
output:
  pdf_document
---
## Scenario

Sršen asks you to analyze smart device usage data in order to gain insight into how consumers use non-Bellabeat smart devices. She then wants you to select one Bellabeat product to apply these insights to in your presentation. These questions
will guide your analysis:
*What are some trends in smart device usage?
*How could these trends apply to Bellabeat customers?
*How could these trends help influence Bellabeat marketing strategy?

## Business task

It's about analyzing any trend concerning Bellabeat customers, and how it will help for growth.

## Data sources used

[FitBit Fitness Tracker Data](www.kaggle.com/arashnic/fitbit) (CC0: Public Domain, dataset made available through [Mobius](www.kaggle.com/arashnic)).Thirty eligible Fitbit users consented to the submission of personal tracker data, including minute-level output for physical activity, heart rate, and sleep monitoring:

## Data cleaning

#### The file used from the data source

```{r}
library(tidyverse)
library(readr)
sleepDay_merged <- read_csv("sleepDay_merged.csv")
as_tibble(sleepDay_merged)
```

#### File cleaning

Excel was used for data cleaning.

```{r echo=TRUE}
library(tidyverse)
library(readr)
Sleep <- read_csv("Sleep.csv")
as_tibble(Sleep)
```

* Id has been transformed to names
* Minutes have been transformed to hours
* Date has been transformed to the number of days

## Analysis

R was used for visualizing the data concerning four members sleep hours.

```{r}
ggplot(data = Sleep)+
  geom_point(mapping = aes(x=Date,y=Sleep,color=ID))+
  facet_wrap(~ID)+
  labs(title = "Hours of sleep",
       subtitle = "A comparison of four persons wearing a Bellabeat product during sleep hours")+
  xlab("Days")+
  ylab("Hours")+
  labs(color="Members")
```

#### Findings

The sleeping hours differ over members, there is no specific attention that the sleeping hours should be between 7-8 hours.

## Recommendations

Based on the information that everyone should sleep 7-8 hours daily, my recommendations are:

* Every member that sleeps less than 7 hours and more than 8 hours, should get a warning message on their device.
* Members should get a message regularly to remember them that they should sleep 7-8 hours.